基于卷积神经网络的视觉目标跟踪算法研究

### 2021-09-27 博士/论文提交/adversarial_attack/TCSVT/大修/response/response.tex

\textbf{We have  replaced ``$A_add$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},$ $\frac{y_0+y_1}{2})$.'' with}
``\uline{$A_{add}$ adds the patch into the search image $\textbf x$ at location $(\frac{x_0+x_1}{2},\frac{y_0+y_1}{2})$.}''
\textbf{in Section III.B of the revised manuscript.}

\textbf{We have replaced ``We evaluate our video-agnostic perturbations for targeted attacks on several tracking benchmarks, i.e., OTB2015 [11], GOT-10k [12], LaSOT [13], UAV123 [13], VOT1016 [14], VOT2018 [15] and VOT2019 [16].'' with}
``\uline{We evaluate our video-agnostic perturbation method for targeted attacks on several tracking benchmarks, i.e., OTB2015 [11], GOT-10k [12], LaSOT [13], VOT2016 [14], VOT2018 [15] and VOT2019 [16].}''
\textbf{in Section IV.A of the revised manuscript.}

\textbf{We have replaced ``We adopt COCO [63], ILSVRC-VID [64] and the training splits of GOT-10k [12] and LaSOT [13] as our training set. (see Table I)'' with}
``\uline{We adopt COCO [63], ILSVRC-VID [64] and the training splits of GOT-10k [12] and LaSOT [13] as our training set.}''
\textbf{in Section IV.B of the revised manuscript.}

\textbf{We have replaced ``Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information.'' with}
``\uline{Similar to CSA, FAN also requires running a generative network for each frame to obtain adversarial information.}''
\textbf{in Section IV.G of the revised manuscript.}

\textbf{We have replaced ``In this paper, we demonstrate that the perturbations and the adversarial patch are both indispensable for attacking trackers and can be jointly optimized in an end-to-end training manner.'' with}
``\uline{In this paper, we demonstrate that the perturbation and the adversarial patch are both indispensable for attacking trackers and can be jointly optimized in an end-to-end training manner.}''
\textbf{in Section III.A of the revised manuscript.}

\textbf{We have replaced ``... to learn the intersection over union (IoU) score of the predicted box $b^{pred}$ and $b^{fake}$ ...'' with}
``\uline{... to learn the intersection over union (IoU) score of the predicted box $b^{pred}_k$ and $b^{fake}_k$. Thus, the fake quality estimation label $\textbf{Q}^*$ at location $(x,y)$ can be expressed as ...}''
\textbf{in Section III.B of the revised manuscript.}

\textbf{We have replaced ``Once the perturbations $(\delta, p)$ are trained, we can use them to perturb the template image and search images of any novel video for attacking.'' with}
``\uline{Once the perturbations $(\delta, p)$ are trained, we can use them to perturb the template and search images of any novel video for attacking.}''
\textbf{in Section III.C of the revised manuscript.}

### 2021-09-28 博士/毕业论文/ucasthesis/Tex/Chap_globally.tex
删除多余的字：指

UAV20L \cite{mueller2016benchmark} 是从低空鸟瞰视角捕获的航拍视频数据集。UAV20L 数据库专为长期跟踪而设计，包含 20 个视频，平均长度为 2934 帧。
遵循 OTB50 \cite{OTB} 的评估方法，我们使用精确度和成功率来评估 UAV20L 数据集上跟踪器的性能。精确度反映了指从预测边界框的中心点到真实边界框的中心点的距离。成功率使用预测边界框与真实边界框的边框重叠计算得到。在图 \ref{fig:globally_uav20l} 中，不同跟踪器的性能比较通过精度图和成功图进行可视化。

>>>>

UAV20L \cite{mueller2016benchmark} 是从低空鸟瞰视角捕获的航拍视频数据集。UAV20L 数据库专为长期跟踪而设计，包含 20 个视频，平均长度为 2934 帧。
遵循 OTB50 \cite{OTB} 的评估方法，我们使用精确度和成功率来评估 UAV20L 数据集上跟踪器的性能。精确度反映了从预测边界框的中心点到真实边界框的中心点的距离。成功率使用预测边界框与真实边界框的边框重叠计算得到。在图 \ref{fig:globally_uav20l} 中，不同跟踪器的性能比较通过精度图和成功图进行可视化。
